---
title: "R Notebook"
output: html_notebook
---

```{r}
##loading the data and libraries 
library(tidyverse)
library(janitor)

neighbourhood_rating <- read_csv("../raw_data/neighbourhood_rating.csv") %>% 
  clean_names()
green_spaces <- read_csv("../raw_data/green_spaces.csv") %>% 
  clean_names()
community_belonging <-read_csv("../raw_data/community_belonging.csv") %>% 
  clean_names()
```

#Great! No missing values in my data
```{r}
#checking missing values 
green_spaces %>%
  summarise(count = sum(is.na(green_spaces_joined)))

community_belonging %>% 
  summarise(count = sum(is.na(community_belonging)))

neighbourhood_rating %>% 
  summarise(count = sum(is.na(neighbourhood_rating)))
```


```{r}
#council areas codes data
council_areas <- read_csv("../raw_data/967937c4-8d67-4f39-974f-fd58c4acfda5.csv") %>% 
  clean_names()
```

```{r}
#dropping variables I don't need 
council_areas<- council_areas %>% 
  select(ca, ca_name)

#renaming feature_code column for joining
council_areas %>% 
  rename(feature_code = ca)
#checking for missing values
council_areas %>% 
  summarise(count = sum(is.na(council_areas)))
```

```{r}
#joining datasets to council area data
green_spaces_joined <- inner_join(
  green_spaces, council_areas, by = c("feature_code" = "ca"))
community_belonging_joined <- inner_join(
  community_belonging, council_areas, by = c("feature_code" = "ca"))
neighbourhood_rating_joined <-  inner_join(
  neighbourhood_rating, council_areas, by = c("feature_code" = "ca"))
```



```{r}
#factoring green_spaces variables for plotting 
green_spaces_joined %>% 
  mutate(age = factor(age, levels = c("16-34 years", "35-64 years",
                                      "65 years and over", "All")),
         simd_quintiles = factor(simd_quintiles, levels = c("20% most deprived",
                                                            "80% least deprived",
                                                            "All")),
         distance_to_nearest_green_or_blue_space = factor(
           distance_to_nearest_green_or_blue_space, levels = c(
             "A 5 minute walk or less",
             "Within a 6-10 minute walk",
             "An 11 minute walk or more",
             "Don't Know"
           )
         )) 
```

#Are there certain groups that have local access to green space? 
#Are there groups that are lacking access? 
#What is the big difference in how far people have to walk to access their green space? 


```{r}
#plotting simd_quintiles for every year to see if there're significant 
#differences for each year
#Filtering out Simd_quintiles == "All"
green_spaces_joined %>% 
  filter(simd_quintiles != "All") %>% 
ggplot(aes(x = distance_to_nearest_green_or_blue_space, fill = simd_quintiles))+
  geom_bar(position = "dodge")+
  facet_wrap(~date_code)
```

```{r}
#simd quinitles and distance to green spaces
green_spaces_joined %>%
  filter(simd_quintiles != "All") %>% 
    group_by(simd_quintiles, distance_to_nearest_green_or_blue_space) %>% 
    summarise(mean_percentage = mean(value)) %>% 
  ggplot(aes(x = simd_quintiles, y = mean_percentage, fill = distance_to_nearest_green_or_blue_space))+
  geom_col(position = "dodge")
```

```{r}
#type of tenure and distance to nearest green space
green_spaces_joined %>% 
 filter(type_of_tenure != "All") %>% 
     group_by(type_of_tenure, distance_to_nearest_green_or_blue_space) %>% 
    summarise(mean_percentage = mean(value)) %>% 
  ggplot(aes(x = type_of_tenure, y = mean_percentage, fill = distance_to_nearest_green_or_blue_space))+
  geom_col(position = "dodge")
```

```{r}
#household type and distance to green spaces
green_spaces_joined %>% 
  filter(household_type != "All") %>% 
    group_by(household_type, distance_to_nearest_green_or_blue_space) %>% 
    summarise(mean_percentage = mean(value)) %>% 
  ggplot(aes(x = household_type, y = mean_percentage, fill = distance_to_nearest_green_or_blue_space))+
  geom_col(position = "dodge")
```

```{r}
#ethnicity and distance to green spaces 
green_spaces_joined %>% 
  filter(ethnicity != "All") %>% 
    group_by(ethnicity, distance_to_nearest_green_or_blue_space) %>% 
    summarise(mean_percentage = mean(value)) %>% 
  ggplot(aes(x = ethnicity, 
             y = mean_percentage, 
             fill = distance_to_nearest_green_or_blue_space))+
  geom_col(position = "dodge")
```

```{r}
#gender and distance to green spaces
green_spaces_joined %>% 
 filter(gender != "All") %>% 
    group_by(gender, distance_to_nearest_green_or_blue_space) %>% 
    summarise(mean_percentage = mean(value)) %>% 
  ggplot(aes(x = gender, 
             y = mean_percentage, 
             fill = distance_to_nearest_green_or_blue_space))+
  geom_col(position = "dodge")
```

```{r}
#urban/ rural areas and distance to green spaces
green_spaces_joined %>% 
 filter(urban_rural_classification != "All") %>% 
    group_by(urban_rural_classification, distance_to_nearest_green_or_blue_space) %>% 
    summarise(mean_percentage = mean(value)) %>% 
  ggplot(aes(x = urban_rural_classification, 
             y = mean_percentage, 
             fill = distance_to_nearest_green_or_blue_space))+
  geom_col(position = "dodge")
```

#How do people in neighbourhoods with good access to green space differ from 
#those who have no good access? Are there differences how they rate their 
#neighbourhoods? Are there differences in how they rate their communities? 

#neighbourhood
```{r}
#all walking distances to nearest green space
neighbourhood_rating_joined %>% 
  filter(walking_distance_to_nearest_greenspace != "All") %>% 
    group_by(neighbourhood_rating, walking_distance_to_nearest_greenspace) %>% 
    summarise(mean_percentage = mean(value)) %>% 
  ggplot(aes(x = neighbourhood_rating, 
             y = mean_percentage, 
             fill = walking_distance_to_nearest_greenspace))+
  geom_col(position = "dodge")
```
```{r}
#very good rating and walking distance to green spaces 
neighbourhood_rating_joined %>% 
  filter(walking_distance_to_nearest_greenspace != "All", 
         neighbourhood_rating == "Very good") %>% 
    group_by(neighbourhood_rating, walking_distance_to_nearest_greenspace) %>% 
    summarise(mean_percentage = mean(value)) %>% 
  ggplot(aes(x = neighbourhood_rating, 
             y = mean_percentage, 
             fill = walking_distance_to_nearest_greenspace))+
  geom_col(position = "dodge")
```
```{r}
#very poor rating and walking distance to green spaces 
neighbourhood_rating_joined %>% 
  filter(walking_distance_to_nearest_greenspace != "All", 
         neighbourhood_rating == "Very poor") %>% 
    group_by(neighbourhood_rating, walking_distance_to_nearest_greenspace) %>% 
    summarise(mean_percentage = mean(value)) %>% 
  ggplot(aes(x = neighbourhood_rating, 
             y = mean_percentage, 
             fill = walking_distance_to_nearest_greenspace))+
  geom_col(position = "dodge")
```
#community
```{r}
#commuity belonging and walking distance to green spaces
community_belonging_joined %>% 
  filter(walking_distance_to_nearest_greenspace != "All") %>% 
    group_by(community_belonging, walking_distance_to_nearest_greenspace) %>% 
    summarise(mean_percentage = mean(value)) %>% 
  ggplot(aes(x = community_belonging, 
             y = mean_percentage, 
             fill = walking_distance_to_nearest_greenspace))+
  geom_col(position = "dodge")
```

##interestngly we can say that communities with higher community belonging are 
#closer to a green space. There is probably a correlation between community 
#rating and neighbourhood rating